TBD

### 2020-11-03 outputs/paper/paper.Rmd
8.29

Key features of data?

>>>>

The dataset that we used contains many key features. For one, a lot of the variables contain an extensive list of options assuring us that the data represents the participant's view accurately. Despite the fact that we cleaned the dataset to make it simpler to view, we still believe that the detailed responses that the participants provided accurately reflect their views on the 2020 election. Another key feature is
